Now that's fresh water: Trends in India from the 1992 Demographic and Health Survey

### 2022-04-01 outputs/graphs.Rmd
filtered out unneeded vars

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(DiagrammeR)
library(reshape2)

dhs <- readr::read_csv(here::here("inputs/data/cleaned_data.csv"))
dhs <- dhs %>%
  select(states, everything())
# TODO: delete after complete
view(dhs)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(DiagrammeR)
library(reshape2)
library(here)
library(knitr)

dhs <- read_csv(here::here("inputs/data/cleaned_data.csv"), show_col_types = FALSE)
```

@@

```{r}
tiny_dhs <- dhs |>
  select(c(1, 2, 4, 14, 16, 19))
```

### 2022-04-01 outputs/paper/paper.Rmd
filtered out unneeded vars

---
title: "Looking at the India State Findings frm the 1992 DHS Final Report"
subtitle: ""
author: 
  - Bilal Haq
  - Ritvik Puri
thanks: "Code and data are available at: https://github.com/haqbilal/India-1992-DHS-State-Findings"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

>>>>

---
title: "Now that's fresh water: Trends in India from the 1992 Demographic and Health Survey"
subtitle: ""
author: 
  - Bilal Haq
  - Ritvik Puri
thanks: "Code and data are available at: https://github.com/haqbilal/India-1992-DHS-State-Findings"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: references.bib
---
